Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-04 paper.qmd
Found the best UMAP view which contain three clusters as well for PBMC3k

```{r}
#| label: load-libraries
#| warning: false
#| echo: false
# remotes::install_github("JayaniLakshika/quollr")
library(quollr)
library(tibble)
library(dplyr)
# remotes::install_github("jlmelville/snedata")
library(snedata)
library(ggflowchart)
library(purrr) ## map function
library(gridExtra) ## for grid.arrange
library(rsample)
library(DT)
library(ggbeeswarm)
library(ggplot2)
library(readr)
library(tidyr)

@@

umap_pbmc <- read_rds("data/pbmc3k/pbmc_umap_15_min_dist_0.99.rds")
nldr3 <- umap_pbmc |>
  ggplot(aes(x = UMAP1,
             y = UMAP2))+
  geom_point(alpha=0.1, size=1, colour=clr_choice) +
  interior_annotation("c")

>>>>

```{r}
#| label: load-libraries
#| warning: false
#| echo: false
# remotes::install_github("JayaniLakshika/quollr")
library(quollr)
library(tibble)
library(dplyr)
# remotes::install_github("jlmelville/snedata")
# library(snedata)
# library(ggflowchart)
#library(purrr) ## map function
#library(gridExtra) ## for grid.arrange
# library(rsample)
# library(DT)
library(ggbeeswarm)
library(ggplot2)
library(readr)
library(tidyr)

@@

#umap_pbmc <- read_rds("data/pbmc3k/pbmc_umap_15_min_dist_0.99.rds")
umap_pbmc <- read_rds("data/pbmc3k/pbmc_umap_12_min_dist_0.99.rds")
nldr3 <- umap_pbmc |>
  ggplot(aes(x = UMAP1,
             y = UMAP2))+
  geom_point(alpha=0.1, size=1, colour=clr_choice) +
  interior_annotation("c")
